---
title: "AirBnB Supply Dashboard"
author: "By Anonymous Analyst Extraordinaire"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: united
---

```{r}
# INSTRUCTIONS
# 1. Click the `knit` button at the top of RStudio and observe the result. If you see a dashboard, then are good to go. 
# 2. Now, modify the dashboard: 
	# - Include your names in the `author` metadata up top
	# - Write code for data preparation and visualizations. 
	# - Include all your code in the `R` "code chunks" that begin with ````{r}`
	# - Add commentary in the indicated area
# 4. `knit` your final dashboard one last time and place it in the shared Dropbox folder (link in email)
# 5. **FILL OUT FEEDBACK SURVEY** by copying and pasting the link below into your browser:  
# https://goo.gl/forms/7rqAPMn37DzRqWko2
# 6. Break for lunch! 
```

```{r}
# You may find the following resources useful: 
# - Your team member(s)! 
# - Data wrangling [cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf), 
# - `R` graphics [cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf), 
# - [`R` Graphics Cookbook](http://www.cookbook-r.com/Graphs/)
```

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
```

```{r data_prep}
# put your data preparation code here. To get you started, the data preparation we performed in the session previously has already been pasted in. Feel free to add any additional data preparation code needed for your visualizations

listings <- read_csv('../data/listings.csv')
calendar <- read_csv('../data/calendar.csv')

current_table <- calendar %>% 
	filter(!is.na(price), 
		   date < lubridate::today(),
		   date > lubridate::mdy('6/1/2016')) %>%
	group_by(listing_id) %>% 
	summarise(last_active = max(date))

recent_listings <- listings %>% 
	left_join(current_table, by = c('id' = 'listing_id')) %>% 
	filter(last_active > lubridate::mdy('6/1/2016'))

summary_table <- recent_listings %>% 
	mutate(price = price %>% gsub('\\$|,', '',.) %>% as.numeric(),
		   price_per = price / accommodates,
		   weekly_price = weekly_price %>% gsub('\\$|,', '',.) %>% as.numeric(),
		   weekly_price_per = weekly_price / accommodates)  %>% 
	group_by(neighbourhood, property_type) %>% 
	summarize(n = n(), 
			  mean_rating = mean(review_scores_rating, na.rm = TRUE),
			  price_per = mean(price_per, na.rm = TRUE),
			  weekly_price_per = mean(weekly_price_per, na.rm = T),
			  capacity = sum(beds)) %>% 
	ungroup()
```


# Descriptive Analysis


Column {data-width=650}
-----------------------------------------------------------------------

### Box 1

```{r box_1}
# Put the code for your main visualization here. A high-quality main visualization will likely use `color`, `fill`, or `facet_wrap` to make help decision-makers make comparisons between different categories.  
# 
listings %>% 
	filter(number_of_reviews < 100) %>%
	ggplot() + 
	aes(x = number_of_reviews, y = review_scores_rating, color = property_type) + 
	geom_point(alpha = .5) + 
	theme_bw() + 
	### <b>
	facet_wrap(~property_type) + 
	### </b>
	labs(x='Number of Reviews', y='Review Score', title='Review Volume and Review Quality') + 
	guides(color = FALSE)
```

Column {data-width=350}
-----------------------------------------------------------------------

### Box 2

Frequently, visualization for decision-makers are most useful when accompanied by analysis, interpretation, and sometimes a recommendation by the analyst. Feel free to fill in your own commentary on your visualizations in this box or the one below. You can leave the `R` code chunk blank for your commentary box. 

```{r box_2}

```

### Box 3

```{r box_3}
# Put the code for a supporting visualization here. This visualization should add context and nuance, but expect the main visualization to convey the bulk of your message. 

summary_table %>% 
	ggplot() + 
	###<b>
	aes(x = reorder(neighbourhood, n), y=n, fill = property_type) + 
	###</b>
	coord_flip() + 
	geom_bar(stat = 'identity') +
	xlab('Neighborhood') + 
	ylab('Number of Listings')
```


# Modeling


Column {data-width=650}
-----------------------------------------------------------------------

### Box 1


Column {data-width=350}
-----------------------------------------------------------------------

### Box 2

