---
title: "AirBnB Supply Dashboard"
author: "By Anonymous Analyst Extraordinaire"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: united
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
```



```{r data_prep}
# put your data preparation code here. To get you started, the data preparation we performed in the session previously has already been pasted in. 

```

Column {data-width=650}
-----------------------------------------------------------------------

### Box 1
Put the code for your main visualization here. 
```{r box_1}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Box 2

Frequently, visualization for decision-makers are most useful when accompanied by analysis, interpretation, and sometimes a recommendation by the analyst. Feel free to fill in your own commentary on your visualizations in this box or the one below. You can leave the `r` code chunk blank for your commentary box. 

```{r box_2}

```

### Box 3
Put the code for a supporting visualization here. This visualization should add context and nuance, but expect the main visualization to convey the bulk of your message. 
```{r box_3}

```

