---
title: "Deep Learning Pre-Assignment"
output:
  word_document: default
  html_document: default
---

First, please download the following package in R using the commands below:

```{r, eval=FALSE}
install.packages("keras")
```

Next we need to get the core packages that the Keras API relies upon installed on your machine. To do this, execute the commands

```{r, eval=FALSE}
library(keras)
install_keras()
```

Finally, to ensure that Keras has been properly installed and that it's ready to be used for the lesson, please execute the following commands. You should see 10 progress bars. Please email me at zblanks@mit.edu if you do not see this.

```{r, eval=FALSE}
library(keras)

# Generate some toy data 
x <- runif(n = 100)
y <- (0.1 * x) + 0.3

# Define our computational graph
model <- keras_model_sequential() %>% 
  layer_dense(units = 1, input_shape = c(NULL, 1))

# Define the model compiler
model %>% compile(
  loss = "mean_squared_error",
  optimizer = optimizer_sgd()
)

# Fit the model to the data
model %>% fit(
  x = x, y = y, epochs = 10, verbose = 1
)
```

