---
title: "Control Flow"
author: "Colin Pawlowski"
date: "October 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
In this document, we go over if-else statements, for-loops, and functions in R.  
Often times, you will not use these, because you can rely upon packages such as
`tidyverse` which have many built-in functions that can do everything that
you need. However, these are good to know as a fall-back option if you want
to do more advanced tasks in R.  

## Control Flow
```{r If statements}
# We can write if-else statements using the notation
# if(<condition>) { 
#   <code here> 
# }
# else {
#   <code here>
# }
# For example:
x <- 8
if (x > 100) {
  print("High")
} else {
  print("Low")
}
```

```{r Multiple If-statements}
# We stack multiple if-else statements as follows:
x <- 68
if (x > 100) {
  print("High")
} else if (x > 50) {
  print("Medium")
} else {
  print("Low")
}
```

## For-loops

```{r }
# We can write for-loops in R using similar notation to the if-statements.
# However, we try to avoid these if possible because for-loops
# are slow in R.
for (i in 1:5) {
  print(paste("Hello World", i))
}
```

## Functions
```{r Functions}
# We can write our own custom functions in R, with the notation:
# myFunc <- function(<arguments here>) {
#   <code here>
#   <return statement>
# }
# For example:
sumPlusDouble <- function(x, y) {
  return(x + 2 * y)
}
sumPlusDouble(1, 2)
sumPlusDouble(x = 1, y = 2)
sumPlusDouble(y = 2, x = 1)
```

```{r Vectorized functions}
# To make a version of the function that will work on vectors, we use
# the command Vectorize().  For example:
sumPlusDoubleVec <- Vectorize(sumPlusDouble)
sumPlusDoubleVec(x = c(1, 8), y = c(2, 50))
```

```{r Applying functions to lists}
# To apply a function to elements of a list, we use the command
# lapply() or sapply(), depending upon if we want to return a list or
# a vector.
x <- list(c(1:10), c(1:3), 3 * c(1:3))
lapply(x, sum) # returns a list
sapply(x, sum) # returns a vector
```

```{r Anonymous functions}
# Sometimes, it is convenient to define functions within an sapply()
# or lapply() function only.  In this case, we can use "anonymous" functions.
# Also note that the {} and return statements are unnecessary.
sapply(x, function(x) { return(2 * length(x)) })
sapply(x, function(x) return(2 * length(x)))
sapply(x, function(x) { 2 * length(x) })
sapply(x, function(x) 2 * length(x))
```

## Exercise
```{r Exercise}
# Read in the Airbnb reviews from the following file.
# Count up the number of unique elements in each column of
# the data frame.  (Hint: the data frame is a list.)
library(data.table)
reviews <- fread("data/reviews.csv", sep = ",")
```
