---
title: "Tidyverse"
author: "Colin Pawlowski"
date: "October 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
In this document, we review the `tidyverse` package which was taught
during the orientation week.  This is in one of the most popular software 
packages in all of data science.  We go over some of the most useful functions,
and also some syntax which is most confusing.  In addition, now that you have
been exposed to Julia, Python, and SQL, you can get a good sense of the
advantages of R for simple data wrangling tasks.  

Let's begin by reading in the data.  We use data.table, because this
is the fastest way to read in CSV files.  
```{r readdata}
library(data.table)
reviews <- fread("data/reviews.csv", sep = ",")
system.time(listings <- fread("data/listings.csv", sep = ","))
```

Let's check how much slower it would have been if we use the standard
read.csv function in R:
```{r readdataslow}
system.time(listings <- read.csv("data/listings.csv"))
```

## Pipe Operator
```{r Pipe operator}
# The pipe operator is the macro which allows us to write f(x) as:
# x %>% f
# This is useful because using it allows us to chain commands, and
# makes the R code look more like SQL code.
# For example, this code counts the number of
# missing values in each column:
library(tidyverse)
listings %>%
  sapply(function(x) sum(is.na(x)))
```

## Head
```{r Head}
# Return the top K rows of a data frame with head(K)
listings %>%
  head(2)
```

## Select
```{r Select}
# We can select, reorder, and rename columns with select():
listings %>%
  select(Website = listing_url, ID = id) %>%
  head(2)
```

## Mutate
```{r Mutate}
# We can modify columns with mutate:
listings %>%
  select(price) %>%
  mutate(price = gsub("\\$|,", "", price)) %>%
  head()
```

## Group-by and Summarize
```{r Group_by and Summarize}
# We can perform operations on subsets of the data set with group_by
# and summarize.  For example, if we want to compute the average price
# of each neighborhood in Boston:
listings %>%
  select(neighbourhood_cleansed, price) %>%
  mutate(price = gsub("\\$|,", "", price)) %>%
  mutate(price = as.numeric(price)) %>%
  group_by(neighbourhood_cleansed) %>%
  summarize(price = mean(price)) %>%
  ungroup()
```

## Joins
Next, let's see how we can join two different data frames together.
```{r Joins}
# We can use the function 
# left_join(<data set 1>, <data set 2>, by = (<id 1> = <id 2>))
# to join two data sets together. Let's use this function to add the
# "review_scores_rating" from the listings data frame
# to the reviews data frame. 
listingsSub <- listings %>%
  select(id, review_scores_rating)
reviewsExtra <- reviews %>%
  left_join(listingsSub, by = c("listing_id" = "id"))
```

Finally, for this problem, let's add in another column to listingsSub
which classifies the rating for the Airbnb into one of 5 categories.
```{r Convert Rating}
convert_rating <- function(rating) {
  if (is.na(rating)) {
    return("Terrible")
  } else if (rating == 100) {
    return("Perfect")
  } else if (rating >= 95) {
    return("High")
  } else if (rating >= 90) {
    return("Mid")
  } else if (rating >= 80) {
    return("Low")
  } else {
    return("Terrible")
  }
}
convert_rating_vec <- Vectorize(convert_rating)
listingsSub <- listings %>%
  select(id, review_scores_rating) %>%
  mutate(review_scores_category = convert_rating_vec(review_scores_rating))
```

## Exercise
```{r Exercise}
# Starting from the data frames "reviews" and "listingsSub",
# create a data frame that we can use to predict the 
# average review score rating from the raw text of the reviews.
# The final data frame should have one row per listing, with
# these four columns in the following order:
# 1) listing_id
# 2) review_scores_rating
# 3) review_scores_category
# 4) comments (which includes all comments for that listing)
# (Hint: use the paste() function inside of summarize to aggregate
# the comments for each listing)
```
